Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-23 WSSSPE3/report/wg_appendix_best_practices.tex
Appendix D: Fix typos.
Appendix D: Added line breaks.
Appendix D:  Small changes.

Core questions that will need to be explored are in knowledge management, 
(transitions between people), reliability (reproducibility), usability, and how a software tool becomes part of the core workflow of well identified users (stakeholders)
relating to tool success and hence sustainability. \katznote{prev sentence is complex and awkward} Ideas 
that may need to be explored include:
\begin{itemize}
\item Requirements engineering to create tools with immediate uptake;
\item When should software ``die''?
\item Catering to disruptive developments in environment e.g.(new hardware, new methodology) ;
\item Dimensions of sustainability -- economic, technical, environmental, 
declining interest in primary application area), \katznote{not sure what the prev. comment goes with} social.
\end{itemize}

Sustainability requires community participation in code development and/or a wide adoption of software.
The larger the community base is using a piece of software, the better are the funding possibilities and thus also the sustainability options.
Additionally developer commitment to an application is essential and experience shows that software packages with an evangelist imposing strong inspiration and discipline are more likely to achieve sustainability.
While a single person can push sustainability to a certain level, open source software also needs sustained commitment from the developer community.
Such sustained commitments include diverse tasks and roles, which can be fulfilled by diverse developers with different knowledge levels.
Besides developing software and appropriate software management with measures for extensibility and scalability of the software, active (expertise) support for users via a user forum with a quick turnaround is crucial.
The barrier to entry for the community as users as well as developers has to be as low as possible.

@@

The key next steps are to write the introduction, reach out to the co-authors, and to agree on the scope of the white paper.

@@

Sandra Gesing and Abani Patra are the main editors and will organize the overall communication and paper. Sections will be assigned to diverse co-authors.

@@

At the moment we don't see any further requirements.

\subsection{Key Milestones and Responsible Parties}
\begin{itemize}
\item 15 Nov: Introduction and scope finished (Abani Patra/Sandra Gesing)
\item 15 Nov: Sections assigned (Abani Patra/Sandra Gesing)
\item 31 Jan: Analyzing funding possibilities for survey
\item 31 Jan: First versions of section
\item 15 Feb: Distribution to WSSSPE community
\item 31 Mar: Final version of white paper
\item 30 Apr: Submission of peer-reviewed paper?
\end{itemize}

>>>>

Core questions that will need to be explored are in knowledge management, 
(transitions between people), reliability (reproducibility), usability, and how a software tool becomes part of the core workflow of well identified users (stakeholders)
relating to tool success and hence sustainability. \katznote{prev sentence is complex and awkward} Ideas 
that may need to be explored include:
\begin{itemize}

\item Requirements engineering to create tools with immediate uptake;

\item When should software ``die''?

\item Catering to disruptive developments in environment, e.g., new hardware,
new methodology;

\item Dimensions of sustainability -- economic, technical, environmental,
declining interest in primary application area), \katznote{not sure what the
prev. comment goes with} social.

Sustainability requires community participation in code development and/or a
wide adoption of software. The larger the community base is using a piece of
software, the better are the funding possibilities and thus also the
sustainability options. Additionally,  developers’ commitment to an application is
essential and experience shows that software packages with an evangelist
imposing strong inspiration and discipline are more likely to achieve
sustainability. While a single person can push sustainability to a certain
level, open source software also needs sustained commitment from the developer
community. Such sustained commitments include diverse tasks and roles, which can
be fulfilled by diverse developers with different knowledge levels. Besides
developing software and appropriate software management with measures for
extensibility and scalability of the software, active (expertise) support for
users via a user forum with a quick turnaround is crucial. The barrier to entry
for the community as users as well as developers has to be as low as possible.

@@

The key next steps are to write an introduction, reach out to the co-authors,
and to agree on the scope of the white paper.

@@

Sandra Gesing and Abani Patra are the main editors and will organize the overall
communication and the paper. Sections will be assigned to diverse co-authors.

@@

At the moment we do not see any further requirements.

\subsection{Key Milestones and Responsible Parties}
\begin{itemize}
\item 15 Nov: Introduction and scope finished (Abani Patra/Sandra Gesing)
\item 15 Nov: Sections assigned (Abani Patra/Sandra Gesing)
\item 31 Jan: Analyzing funding possibilities for survey
\item 31 Jan: First version of each section
\item 15 Feb: Distribution to the WSSSPE community
\item 31 Mar: Final version of the white paper
\item 30 Apr: Submission to a peer-reviewed journal?
\end{itemize}
